---
title: "Linreg Vignette"
author: Maxime Bonneau, Niclas Lovsjö
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linreg Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
##Description
Linreg is a package that performs linear regression. It takes a *formula* of the form *Y~**X***, where **X** and **Y** are vector-valued, and a *data-frame* from which we can take the values of **Y** and **X**. 

### Attributes:
The function *Linreg* returns a list of the class *Linreg*, having the elements: coefficients, resid, df.residual,rank, call, fitted.values, rstudent. 

### Methods:   
  *     resid(X):    
             Gives the residuals as a vector.  
  *     pred(X, Z):    
        Gives the predicted values of the linear model X for the values of the variable Z.  
  *     print(X):  
        Returns the called formula and the estimate of the coefficients.  
  *     plot(X):  
        Plots the Residuals vs. fitted values and Scale-location.  
  *     coef(X):  
        Returns a named vector of the estimate of the coefficients.  

```{r}
X<-linreg(iris$Petal.Length~iris$Sepal.Length,data=iris)
plot(X)
```


> "He who uses Linreg, might just as well use lm ~ Unknown thinker"


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
